---
title: "Scatterplot"
output: html_document
---
A scatter plot is a set of points plotted on a horizontal and vertical axes. It enables us two compare two sets of data.Let’s take the homeruns and strikeouts from the Lahman database of baseball statistics and make a scatterplot!

First, we need to load our libraries. This tells the computer what sets of data to look at!
```{r}
library(Lahman)
library(sqldf)
library(ggplot2)
```

Next, we are going to specify what we are looking for. In this case, career homeruns and strikeouts from players who had more than 400 homeruns. Only the best for us.
```{r}
query<-"SELECT playerID,sum(HR),sum(SO)
FROM Batting 
GROUP BY playerID
HAVING sum(HR)>400"
sqldf(query)
```

We have the information. Save it as a result for ease of use.

```{r}
query<-"SELECT playerID,sum(HR) AS CareerHR,sum(SO) AS CareerSO
FROM Batting
GROUP BY playerID
HAVING sum(HR)>400"
result<-sqldf(query)
```

Okay, now the data pairs turn into points by associating homeruns with the y-axis and strikeouts with the x-axis. We are also going to add the graph title and axis labels in one fell swoop. Things are nicely distinct and easy to see with the ggplot2 coding.

```{r}
ggplot()+
geom_point(data=result,aes(x=CareerSO,y=CareerHR),size=3)+
ggtitle("Career Strikeouts and Homeruns - The Best")+
xlab("Career Strikeouts")+
ylab("Career Homeruns")
```

